{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-11 thesis/thesis.tex
ack nisei

Lastly,
the Android: Netrunner community has become such an important part of my life
over the last half decade or so.
%for the better part of my time as a grad student.
Netrunner is a deckbuilding strategy card game
that depicts cyberspace hacking battles (completely different from real-life computer security)
alongside dystopian social issues (becoming strangely more familiar with each passing year).
Its characters have a diversity of ethnicity and gender identity %and sexual orientation
unparalleled in any other game I know of,
and the community that has grown around it reflects those values.
I thank especially the other Stimhack moderators,
the members of {\sf \#rainbow-coalition},
and the local Pittsburgh crew
for their support, encouragement,
and mutual exchange of inclusive values in these turbulent yet hopeful times.
%and
%friendships very real and deep, even when forged only in text,
%%\footnote{and Slack emojis},
%that will long outlive the silly card game that brought us together.
%%It'd be an injustice to list only a few names here and omit others, but you know who you are.
}

>>>>

Lastly,
the Android: Netrunner community has become such an important part of my life
over the last half decade or so.
%for the better part of my time as a grad student.
Netrunner is a deckbuilding strategy card game
that depicts cyberspace hacking battles (completely different from real-life computer security)
alongside dystopian social issues (becoming strangely more familiar with each passing year).
Its characters have a diversity of ethnicity and gender identity %and sexual orientation
unparalleled in any other game I know of,
and the community that has grown around it reflects those values.
I thank especially the other Stimhack moderators,
%the members of
{\sf \#rainbow-coalition},
Nisei,
and the local Pittsburgh crew
for their support, encouragement,
and mutual exchange of inclusive ideals in these turbulent yet hopeful times.
%and
%friendships very real and deep, even when forged only in text,
%%\footnote{and Slack emojis},
%that will long outlive the silly card game that brought us together.
%%It'd be an injustice to list only a few names here and omit others, but you know who you are.
}
